---
title: "Image Grid"
author: "Iain  Emsley"
date: "17/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Image Grid

This is an R Markdown version of the image grid. 

```{r read}
cooccur <- read.csv('tcat.csv', stringsAsFactors = FALSE)
head(cooccur)
```

Filter the text using a list of terms from the location to identify tweets that contain the terms in the home location. Filtered contains the subset of location tweets that match the terms. 

```{r filterTags}
termsToFind <- c('at home', 'house', 'household', 'finger prick')

tcat <- data.frame()

filtered <- cooccur[grep( "at home|house|household|finger prick", cooccur$text, ignore.case = TRUE),]
head(filtered)
#tcat <- filtered$media_urls
#head(tcat)
```
Filter the locations by an issue. Here the inequality issue is used to further filter the location by the issue.
```{r runissue}
imagegrid = data.frame()

issues <- filtered[grep("wealth|gated|access|insurance|unequal|racism|racial breakdown", filtered$text, ignore.case = TRUE),]
```

```{r createImageGrid}  
  split_media<- lapply(issues$media_urls, function (x) strsplit(as.character(x),';',fixed=TRUE))

  split_file<- lapply(split_media, function (x) {
    if (x != 'character(0)') {
    f = strsplit(as.character(x),'/',fixed=TRUE); 
    g = tail(as.character(f[[1]]), n=1);
    gsub('")', '', g)
    }
  })
  
  for  (down in split_file) {
    y  <- paste('data', down,sep = '/')
    if (!file.exists(y) && y != 'character(0)') {
      download.file(down, y, mode='wb')
    }
  }
  
  count = table(unlist(split_file))
  
  #images = as.data.frame(count)
  imagegrid = rbind(as.data.frame(count))
  #write.csv(image, term + ".csv")

imagegrid$figure <- lapply(imagegrid$Var1, function(x) paste("![](data/", x, ")", sep=''))
knitr::kable(imagegrid)
```

## Clean Data

Split the columns where they contain a ';'. 

Create the file name by getting the final part of the url from the dataframe.

## Export data

Convert the table into a data frame. 
